Suppose you are Google and you assign a vector to each possible document. When
a user searches for a term, you want to collect some vectors that are indicative of that search term. You also want to be diverse, e.g., if a user searches for "jaguar" you want to return some documents with cars and others with the animal. We could model this by returning vectors that are linearly independent.

\begin{itemize}
	\item \textbf{Inputs:} vectors $(v_1, v_2, \cdots, v_n)$ with weights 
$(w_1, w_2, \cdots, w_n)$.
    \item \textbf{Goal:} Find a basis for the space spanned by $(v_1, v_2, \cdots, 
v_n)$ of maximum total weights.
\end{itemize}
\paragraph{Note.} A single vector is linear independent to any other vector if 
it is a zero vector.

\subsection{Greedy Algorithm}
\begin{itemize}
	\item Sort vectors and renaming them by descending order of weights.
	\item $S$ is an empty set of vectors initially.
	\item For each vectors $v_i$ in this order, if $S \cup \{v_i\}$ is linearly 
independent and $v_i$ is an non-zero vector, then $S = S \cup \{v_i\}$.
\end{itemize}

\subsection{Correctness}
\begin{theorem}
	\textbf{(Exchange Property)} Suppose A and B are finite subset of linearly independent vectors in $ \mathbb{R}^d $, and suppose $ |A| < |B| $. $\exists b \in B$, such that $ A \cup \{b\} $ in linearly independent.
\end{theorem}

\begin{proof}
	Indeed, there must be a vector in $ B $ that lies outside the space spanned by $ A $ because of the dimensions of space $ <B> $ and $ <A> $.
\end{proof}

\begin{theorem}
	\textbf{(Hereditary property)}. If $ R \subset S $ and $S$ is a linearly independent set of vectors, then $R$ is also linearly independent.
\end{theorem}

Greedy algorithm for finding a maximum of basis works because of vector has the exchange and hereditary properties.

\begin{itemize}
	\item Suppose greedy returns vectors $G = \{v_{i1}, v_{i2}, \cdots, v_{ik}\}$.
	\item Suppose, for contradiction, there is an optimal solution that return $O = \{v_{j1}, v_{j2}, \cdots, v_{jk} \}$, which has a better total of weights.
\end{itemize}

\begin{claim}
	$G$ is at least as good as $ O $.
\end{claim}
\begin{claimproof}
	
	Let $ v_{il} $ be the first vector chosen by greedy algorithm that is not in $O$. Let $ A = \{v_{i1}, \cdots, v_{il}\} $, $ B = O$. 
	
	Hence,
	\begin{itemize}
		\item If $ l = k $, $ G $ is at least as good as $ O $.
		\item If $ l < k $, $ |A| < |B| = k $. By exchange property, applied repeatedly, we can keep adding vectors from $ B $ to $ A $ while preserving linear independent to $ A $ until $ |A| = |B| $. In the end, after borrowing some elements from $B$, the only difference between $A$ and $B$ is that $ A $ has $ v_{il} $ instead of some vectors from $B$. Moreover, that vector has weight $ \le w_{il} $. So $ w(A) \ge w(O)$.
		
		Note that even if $ w(A) = w(O) $, $ A $ agrees still more with greedy algorithm than $ O $. Suppose in the ``worest case'', no matter how to choose $l$, the weight of expanded $A$ always equal to the weight of $B$. We are still able to prove that greedy algorithm is as good as $ O $ by induction. So the claim still holds.
	\end{itemize}
	
%	Since the $v_j$'s form a basis,
%	\[v_{i1} = \alpha_1 v_{j1} + \alpha_2 v_{j2} + \cdots + \alpha_k v_{jk}\]
%	
%	$v_{i1}$ is chosen by greedy algorithm so it is not a zero vector. Therefore, 
%	there must be some $\alpha_l$ is non-zero.
%	
%	We can add $v_{i1}$ to the set $(v_{j1}, v_{j2}, \cdots, v_{jk})$ and kick out 
%	$v_{jl}$.
\end{claimproof}





